Parallel Tractability of Ontology\\ Materialization: Technique and Practice

### 2018-02-22 parallel-tractability-J-v9/appendix.tex
revised the eval section
checking appendix

\textbf{Lemma~\ref{lemma:a1}}
\emph{Given a datalog program $P=\langle R, \textbf{I}\rangle$, we have
(1) $\mathsf{A}_{bsc}$ halts and returns a materialization graph $\mathcal{G}$ of $P$;
(2) $\mathcal{G}$ has the the minimum depth among all the materialization graphs of $P$.}\\

>>>>

\textbf{Lemma~\ref{lemma:a1}}
\emph{Given a datalog program $P=\langle R, \textbf{I}\rangle$, we have
(1) $\mathsf{A}_{\text{bsc}}$ halts and returns a materialization graph $\mathcal{G}$ of $P$;
(2) $\mathcal{G}$ has the the minimum depth among all the materialization graphs of $P$.}\\
